PK object batch mode trial

### 2023-07-17 data-raw/batchMode_trial_gpm.Rmd
Updated tkstats mthods default behavior

my_predata <- cvt %>%
  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% c("DTXSID0020442",
                                                              "DTXSID5032600",
                                                              "DTXSID2021103"))
my_predata <- cvt %>%
  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% "DTXSID5032600")

@@

@@

```{r single_fit}
my_pk <- pk(data = cvt) +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = TRUE) +
  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
  # scale_time() +
  # stat_model() + 
  stat_error_model(error_group = vars(Chemical, Species, Reference)) 
# Add Reference for Joint Analysis

@@

my_preds <- inner_join(winmodels, my_preds)
my_tkstats <- inner_join(winmodels, my_tkstats)
my_nca <- get_nca(my_pk,
                  nca_group = vars(Chemical, Species,))
my_nca <- my_nca %>% dplyr::select(-param_sd_z, -param_units) %>%
  pivot_wider(names_from = param_name,
              values_from = param_value)

@@

```{r update_eval_kstats}

my_eval <- left_join(my_tkstats_red, my_nca_red) %>%
  filter(is.finite(AUC_inf.tkstats), is.finite(AUC_inf.nca)) %>%
  group_by(!!!my_pk$settings_data_info$nca_group)

my_eval %>%
  dplyr::select(AUC_inf.tkstats, AUC_inf.nca, Cmax.tkstats, Cmax.nca) %>%
  ungroup(Dose) %>%
  summarize(AUC_inf_RMSE = abs(mean(AUC_inf.tkstats) - mean(AUC_inf.nca)),
            Cmax_RMSE = abs(mean(Cmax.tkstats) - mean(AUC_inf.nca)))

@@

>>>>

my_predata <- cvt %>%
  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% c("DTXSID0020442",
                                                              "DTXSID5032600",
                                                              "DTXSID2021103"))
my_predata <- cvt %>%
  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% "DTXSID1043881")

@@

my_predata <- cvt %>%
  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% c("DTXSID2039336",
                                                              "DTXSID7029904",
                                                              "DTXSID1021087",
                                                              "DTXSID2020682"))

@@

```{r single_fit}
my_pk <- pk(data = my_predata) +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = TRUE) +
  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
  scale_time(new_units = "days") +
  # stat_model() + 
  stat_error_model(error_group = vars(Chemical, Species)) 
# Add Reference for Joint Analysis

@@

my_preds <- inner_join(winmodels, my_preds)
my_tkstats <- inner_join(winmodels, my_tkstats) %>%
  dplyr::select(-TKstats, -Reference) %>% distinct()
my_nca <- get_nca(my_pk,
                  nca_group = vars(Chemical, Species,))
my_nca <- my_nca %>% dplyr::select(-param_sd_z, -param_units) %>%
  pivot_wider(names_from = param_name,
              values_from = param_value)

@@

```{r update_eval_kstats}
devtools::load_all()
my_eval <- eval_tkstats(my_pk)

# To give summary RMSEs of Cmax and AUC...
my_eval <- my_eval %>%
  group_by(method, model, .add = TRUE) %>%
  ungroup(Reference) %>%
  summarize(AUC_inf_RMSE = sqrt((1/n())*(sum(AUC_inf.tkstats - AUC_inf.nca,
                                             na.rm = TRUE)^2)),
            Cmax_RMSE = sqrt((1/n())*(sum(Cmax.tkstats - Cmax.nca,
                                          na.rm = TRUE)^2)),
            .groups = "keep")

my_eval <- my_eval %>%
  mutate(dose_norm = TRUE,
         log10_norm = FALSE,
         scale_time = FALSE,
         Analysis_Type = "Pooled")

ggplot(my_eval,
       aes(x = AUC_inf_RMSE,
           y = Cmax_RMSE)) +
  geom_point()

ggplot(my_eval,
       aes(x = -log10(AUC_inf_RMSE))) +
  geom_histogram(fill = "grey5") +
  facet_grid(cols = vars(method)) +
  labs(x = "Accuracy of AUC",
       y = "Observations") +
  theme(panel.border = element_rect(color = "black", fill = NA, size = 1.5),
        panel.background = element_blank(),
        panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
        strip.background = element_rect(fill = "white"),
        axis.ticks = element_blank(),
        axis.line = element_blank())

@@

```{r eval_Joint}
my_pk <- readRDS("data-raw/all_cvt_pk_JOINT.rds")
my_eval_joint <- eval_tkstats(my_pk)

# To give summary RMSEs of Cmax and AUC...
my_eval_joint <- my_eval_joint %>%
  group_by(method, model, .add = TRUE) %>%
  ungroup(Reference) %>%
  summarize(AUC_inf_RMSE = sqrt((1/n())*(sum(AUC_inf.tkstats - AUC_inf.nca,
                                             na.rm = TRUE)^2)),
            Cmax_RMSE = sqrt((1/n())*(sum(Cmax.tkstats - Cmax.nca,
                                          na.rm = TRUE)^2)),
            .groups = "keep")

my_eval_joint <- my_eval_joint %>%
  mutate(dose_norm = TRUE,
         log10_norm = FALSE,
         scale_time = FALSE,
         Analysis_Type = "Joint")

ggplot(my_eval_joint,
       aes(x = AUC_inf_RMSE,
           y = Cmax_RMSE)) +
  geom_point()

ggplot(my_eval_joint,
       aes(x = -log10(AUC_inf_RMSE))) +
  geom_histogram(fill = "grey5") +
  facet_grid(cols = vars(method)) +
  labs(x = "Accuracy of AUC",
       y = "Observations") +
  theme(panel.border = element_rect(color = "black", fill = NA, size = 1.5),
        panel.background = element_blank(),
        panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
        strip.background = element_rect(fill = "white"),
        axis.ticks = element_blank(),
        axis.line = element_blank())

total_eval <- bind_rows(my_eval, my_eval_joint)

ggplot(total_eval,
       aes(x = AUC_inf_RMSE,
           y = Cmax_RMSE)) +
  geom_point() +
  facet_grid(rows = vars(Analysis_Type))

total_eval %>%
  dplyr::select(!Cmax_RMSE) %>%
  pivot_wider(names_from = Analysis_Type,
              values_from = AUC_inf_RMSE) %>%
  ggplot(aes(x = -log10(Pooled),
             y = -log10(Joint),
             color = Media)) +
  geom_point(alpha = 0.3) +
  geom_abline(slope = 1, linetype = "dashed") +
  facet_grid(rows = vars(model),
             cols = vars(method)) +
  theme(panel.border = element_rect(color = "black", fill = NA, size = 1.5),
        panel.background = element_blank(),
        panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
        strip.background = element_rect(fill = "white"),
        axis.ticks = element_blank(),
        axis.line = element_blank())

total_eval %>%
  dplyr::select(!Cmax_RMSE) %>%
  pivot_wider(names_from = Analysis_Type,
              values_from = AUC_inf_RMSE) %>%
  mutate(ratio = Joint/Pooled) %>%
  filter(!(ratio == 1)) %>% pull(Chemical) %>% unique()
  View()
